---
title: "IBM 6010 Assignment"
format:
  html:
    theme: litera
    font-family: sans-serif;
    font-size: 110%;
    other-links:
      - text: Rogue Fitness
        href: https://www.roguefitness.com/ 
    #code-links:
     #text: Data Import Code
     #icon: file-code
     #href: data-import.py
    
editor: visual
toc: true
toc-title: Contents
toc-location: left
#toc-expand: 2
number-sections: true
number-depth: 2
smooth-scroll: true	
tabsets: true #enable tabsets to present content
embed-resources: true #create self-contained html
anchor-sections: true #hover over a section title to see an anchor link
citations-hover: true #Enable a hover popup that shows the reference information
df-print: kable
code-fold: true #collapse all code blocks
code-tools: true #toggle code blocks on and off globally
code-link: true	#link functions to their online documentation, downlit and xml2 package required
code-overflow: wrap #long code scroll or wrap
code-block-bg: true
code-block-border-left: "#31BAE9"
highlight-style: pygments
execute:
  warning: false
  message: false
comments:
  hypothesis: true
---

```{r setup, include=FALSE}
# Suppress package startup messages
suppressPackageStartupMessages(library(tidyverse))

#The downlit and xml2 packages are required for code linking 
#install.packages("downlit")
#install.packages("xml2")

library(downlit)
library(xml2)


```

# Introduction

The digital marketing plan for [RogueFitness.com](roguefitness.com) aims to maximize ROAS and prioritize channels and marketing efforts that bring in the highest revenue. To increase ROAS from 8.8 to 10:

-   The budget allocated to loyalty building remains the same at 29%.

-   The budget for demand generation is reduced to 3%, down from 9%.

-   The budget allocated to demand harvesting is increased to 68%, from 62%.

    | Funnel Stage      | Budget | Revenue | Budget % | ROAS |
    |-------------------|--------|---------|----------|------|
    | Demand generation |        |         |          |      |
    | Demand harvesting |        |         |          |      |
    | Loyalty building  |        |         |          |      |
    | TOTAL             |        |         |          |      |

    : Monthly budget and revenue per funnel stage

## SEO

The cost of hiring a new SEO specialist is the biggest expenditure in scaling SEO. Based on the exceptional ROAS (22.6) we see in demand harvesting content, we will hire a second SEO specialist with 10.000 USD[^1].

[^1]: seoconsulting.com

### Budget Allocation

::: panel-tabset
## Demand Generation

ROAS is positive yet on the lower end at 200%. It wouldn't make sense to hire a new SEO specialist specifically for this or further divide our existing specialist's time and energy for it. So even though we are getting a second specialist, the time and effort going into demand generation will remain the same. 

## Demand Harvesting

ROAS is the highest among demand harvesting efforts at 2260%. We can hire a second SEO specialist with 10000 USD who will focus solely on Demand Harvesting and produce and optimize more content, increase rankings and the number of keywords we are focusing on.
:::

### Keyword Analysis

To identify SEO opportunities, we use Search Console. Currently, Rogue Fitness shows up on the second page of the SERP for 14 keywords.

```{r}
ranking <- readxl::read_xlsx("ranking.xlsx") #read file in the same working directory

#install.packages("tidyverse")

library(tidyverse)
filtered_ranking <- ranking %>%
  filter(Position > 10 & Position < 20 ) %>% #filter for the results in second page of SERP
   arrange(desc(Impressions)) #sort by most searched
  
filtered_ranking
```
